Using algorithmic skeletons in EcmaScript to parallelize computation in browsers through Web Workers

### 2015-05-24 docs/paper/paper.tex

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{142223} & 328 \\
    1,000 & \textbf{16503.8} &  359 \\
    10,000 & \textbf{1683.8} & 321.8 \\
    100,000 & 169.6 & \textbf{184.4} \\
    1,000,000 & 16.8 & \textbf{34.1} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

@@

An acceptable speedup of approximately \textbf{2x} can be achieved with a relatively large amount of items (\(10E6\)) and performing a computationally expensive computation (generating pseudo-random numbers). Larger speedups might be possible by applying optimizations to the library and there might also be some potential improvements for operations with \verb+SharedArrayBuffer+s as they are likely not optimized, being that they are only an experimental feature in Firefox Nightly.

@@

\subsubsection*{Acknowledgments.}
Thanks to Rosa Wachenhauzer, our tutor, for reviewing this paper and also for all her support and guidance throughout this entire project.

@@

\bibitem{benchmark} Sepia tone transformation benchmark comparison between p-j-s and plain JS, \url{http://jsperf.com/pjs-shared-vs-normal-vs-seq-100/4}

>>>>

\subsection{Results}
The results for the benchmark are the displayed in Tab.~\ref{tab:benchmark}. Based on those results, we created a chart (Figure~\ref{fig:relative}) that shows the relative performance of the parallel approach compared to the sequential one.
\begin{table}
  \centering
  \begin{tabular}{|r|c|c|}
    \hline
    Elements & Serial [ops/sec] & Parallel [ops/sec] \\
    \hline
    100 & \textbf{130572} & 385 \\
    1,000 & \textbf{14697} &  421 \\
    10,000 & \textbf{1469} & 357 \\
    100,000 & 151 & \textbf{188} \\
    1,000,000 & 14 & \textbf{32} \\
    \hline
  \end{tabular}
  \caption{Comparing p-j-s (parallel) and plain JS (serial) performance for an image transformation.}
  \label{tab:benchmark}
\end{table}

@@

An acceptable speedup of approximately \textbf{2.3x} can be achieved with a relatively large amount of items (\(10E6\)) and performing a computationally expensive computation (generating pseudo-random numbers). Larger speedups might be possible by applying optimizations to the library and there might also be some potential improvements for operations with \verb+SharedArrayBuffer+s as they are likely not fully optimized, being that they are only an experimental feature in Firefox Nightly.

@@

\subsubsection*{Acknowledgments.}
Thanks to Rosa Wachenchauzer, our tutor, for reviewing this paper and also for all her support and guidance throughout this entire project.

@@

\bibitem{benchmark} Sepia tone transformation benchmark comparison between p-j-s and plain JS, \url{http://jsperf.com/pjs-map-vs-serial/9}
